%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Knud Martin Hansen}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{birth date}{23, June 1978 (age: 38)} % Email address

\NewEntry{email}{\href{mailto:knud.hansen@gmail.com}{knud.hansen@gmail.com}} % Email address

\NewEntry{phone}{+45 22 63 34 86} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\Description{Highly experienced Embedded Software Engineer. I Have deep knowledge hardware near software, processor architecture, embedded software toolchain. \newline I will extend my experience in embedded software development and architecture to larger real time systems.\newline Fluent in English, French, Danish. Advanced German}\vspace{2em} % Goal text

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2013--Present}{Lead Developer, \textsc{Oticon AS}}{}{Copenhagen, Denmark}

\Description{\MarginText{Role}Led development (15 people) of the firmware platforms for hearing instruments and hearing instrument accessories. Responsible of integrating features to the platform, including task estimation, memory and cycle budgetting. Responsible of multiple chipsets and multiple product support.}
\Description{\MarginText{Achievements}Integrated first Bluetooth Low Energy chip into the Oticon platform.\newline Succesful delivery of a platform for the OPN hearing instrument and accessories.\newline Successful delivery of 4 ROMs.\newline Providing IC requirements for three ICs}
\Description{\MarginText{Tasks}SysML architectural description of the Firmware platform.\newline definition of the Firmware Platform requirements (DOORS).\newline Support for several chipset and firmware configurations.\newline Requirement definition for the Hearing Instrument Integrated Circuits. \newline Definition of Firmware Platform API.\newline Memory budgetting and memory footprint monitoring (python and excel).\newline Implementation (C) and test (C++/java) of firmware features}
\vspace{1em} % Extra space between major sections

%------------------------------------------------

\NewEntry{2005--2013}{Firmware Developer, \textsc{Oticon AS} -- Copenhagen, Denmark}

\Description{\MarginText{Role}Developed platform firmware for control and DSP processors. Developed test framework for IC verfication. IC debugging.}

\Description{\MarginText{Achievements}Implementation of the firmware tool chain for the Aurora chipset.\newline Implementation of a bit-true test framework for the Fusion Chipset.\newline Development of Firmware for the Feedback Cancellation module on the Fusion Chipset.\newline Developed IC validation framework.}

\Description{\MarginText{Tasks}Implementing firmware for the control processor for the Oticon Firmware Platform in C.\newline optimization of the program memory consumption.\newline development of python tools for stack analysis and ROM patching.\newline RTOS evaluation. Porting embOS to the HI processors.\newline Implementing a java framework for validation of ICs including control of instruments and interface to an SQL database including PhP frontend.}

\vspace{1em} % Extra space between major sections

%------------------------------------------------

\NewEntry{2001--2002}{Process Control Engineer, \textsc{Siemens AG} -- Karlsruhe, Germany}

\Description{\MarginText{Role}Developed software for control of a process line.}

\Description{\MarginText{Achievements}Implementation of a module for control of pumps and valves.}

\Description{\MarginText{Tasks}Implementation of a generic STEP7 module for controlling pumps and valves in a chemical production line.\newline Implementation in C++ of a tool to instantiate and setup the module for a production chain.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

Add internships.

\NewEntry{2002-2004}{Technical University of Denmark -- Copenhagen}

\Description{\MarginText{Masters of Science}M.Sc. in Computer Systems Engineering -- System on Chip.\newline 
Masters with focus on IC design, processor architecture and embedded software. 	\newline
Thesis: \textit{Simulation Framework for Wireless Sensor Networks} -- 
Implementating a Model for enabling network level design of sensor networks based on a SystemC (C++) SoC simulation framework.\newline
Supervisor: Prof.~Jan \textsc{Madsen}}

%------------------------------------------------

\NewEntry{1996-2001}{Technical University of Mechanical and Electrical Engineering (E.N.S.E.M.) -- Nancy, France}

\Description{\MarginText{Masters og Engineering}Automated Systems Engineering\newline
Degree with focus on automation, electronics and computer systems in the context of process control.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skills and Competences -- FIXME:find better name}\vspace{1em}

\Description{\MarginText{Architecture}SysML, UML}

\Description{\MarginText{Programming}Assembler, C, C++, Java}

\Description{\MarginText{Scripting}Python, Perl, Bash}

\Description{\MarginText{Version Control}Perforce, Git}

\Description{\MarginText{Build Flow}\textsc{Scons}, Make}

\Description{\MarginText{Other}PHP, SQL, HTML, XML, XSLT, Doxygen, Jenkins}

\Description{\MarginText{HDL}VHDL, System verilog}

\Description{\MarginText{Languages}Fluent: French, English, Danish. Advanced: German}



%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Courses}\vspace{1em}

\Description{\MarginText{}2016: Securing Embedded Systems course - BAAR group}
\Description{\MarginText{}2015: internal Requirement Specification and DOORS courses}
\Description{\MarginText{}2013: SysML system modelling course - FIXME}

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\vspace{1em}

\spacedlowsmallcaps{Other Information}\vspace{1em}

%------------------------------------------------

%\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
%\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here
%
%\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \ \ Mothertongue}%
%
%\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command
%
%\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Fluent}
%
%\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command
%
%\Description{\parbox{\langbox}{\textsc{Danish}}\ \ $\cdotp$\ \ \ Fluent}
%
%\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command
%
%\Description{\parbox{\langbox}{\textsc{German}}\ \ $\cdotp$\ \ \ Advanced}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\Description{\MarginText{Sailing}Active member at \textsc{Hellerup Sailing Club} -- Copenhagen Danmark.}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{{Amator racing once a week during the season.}}
\vspace{-1em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{{Teach navigation course every winter (20-30 students).}}
\vspace{-1em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{{Responsible for boat maintenance (6-meter kiel boat).}}

%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{References}\vspace{1em}

%------------------------------------------------

\vspace{1em}
\Description{\MarginText{Oticon AS}Manager: Bjarne \textsc{Kielsholm Ribalaygua}\ \ $\cdotp$\ \ +1 (000) 111 1111\ \ $\cdotp$\ \ \href{mailto:bkri@oticon.com}{bkri@oticon.com}}
\Description{\MarginText{Oticon AS}System Architect: Thomas \textsc{Gleerup}\ \ $\cdotp$\ \ +1 (000) 111 1111\ \ $\cdotp$\ \ \href{mailto:thgl@oticon.com}{thgl@oticon.com}}

\end{cv}

\end{document}
